---
title: "The RosaMATH5793lab5 Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The RosaMATH5793lab5 Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  fig.align = 'center',
  fig.height = 5,
  fig.width = 7
)
```

```{r setup}
library(RosaMATH5793lab5)
```

# Introduction

This package creates a matrix from a data frame and (invisibly) prints several key items associated with the vector. The package contains an S3 Constructor function as well as a print and summary method. The constructor `sampleG()` returns an invisible list containing the centered matrix, the original data as a matrix, the mean vector, the length, and number of variables. The list has class `samg`. The `print` method returns a named list with the first and last three observations of the displacement vector and the angle measures between them. It also plots a 3D plot of the first three components of the displacement vectors. The final method, `summary` returns a named list containing the value of the general variance, the value of the total variance, the variance-covariance matrix $S$. Further the `eigen()` function is applied, and its results are also printed.

# Example

The `ddt` data set is included in this package. We will use a portion of the data for our example.

```{r}
ddtx <- ddt[1:10, c("LENGTH", "WEIGHT", "DDT")]
ddtx
```

First, we assign an arbitrary name to the constructor functions output list. Notice that the class is printed for the list.

```{r}
l <- sampleG(ddtx)
class(l)
```

Next we can use `print` and `summary` to obtain the information.

```{r}
print(l)
```

```{r}
summary(l)
```
